Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2025-12-22 Edith Zemanick/Sweat Variability/sweat_test_analysis.qmd
update sweat variability tables

    "Mild",
    "Mild",

@@

    "Mild",
    "Severe",

@@

@@

  levels = c("Non-CF", "CFTR-RD or CRMS", "Cystic Fibrosis")

@@

  levels = c("Not CF", "Mild", "Severe", "Unknown")

@@

@@

@@

```{r}
# Fit a multiclass ROC
mc_roc <- multiclass.roc(
  df$Diagnosis,
  df$`Na:Cl`,
  quiet = T,
  levels = c("Non-CF", "CFTR-RD or CRMS", "Cystic Fibrosis")
)
roc_list <- list(
  "Cystic Fibrosis vs. Non-CF" = mc_roc$rocs[[2]],
  "CFTR-RD or CRMS vs. Cystic Fibrosis" = mc_roc$rocs[[3]],
  "CFTR-RD or CRMS vs. Non-CF" = mc_roc$rocs[[1]]
)
ggroc(roc_list, legacy.axes = T) +
  theme_bw() +
  theme(legend.title = element_blank())
roc_table <- lapply(roc_list, function(r) {
  coords(
    r,
    "best",
    best.method = "youden",
    ret = c(
      "threshold",
      "sensitivity",
      "specificity",
      "accuracy",
      "tpr",
      "fpr",
      "tnr",
      "fnr"
    )
  )
})
roc_table <- do.call(rbind, roc_table)
kable(roc_table, digits = 3)
```

@@

```{r}
plot(
  roc_list[[2]],
  print.auc = T,
  print.thres = T,
  main = "Cystic Fibrosis vs. CFTR-RD or CRMS"
)
plot(
  roc_list[[1]],
  print.auc = T,
  print.thres = T,
  main = "Cystic Fibrosis vs. Non-CF"
)
plot(
  roc_list[[3]],
  print.auc = T,
  print.thres = T,
  main = "CFTR-RD or CRMS vs. Non-CF"
)
```

@@

```{r}
# Fit a multiclass ROC
gr_roc <- roc(
  `Genotype Risk` ~ `Na:Cl`,
  data = df,
  levels = c("Mild", "Severe"),
  quiet = T
)
plot(
  gr_roc,
  print.auc = T,
  print.thres = T,
  main = "Mild vs. Severe Genotype"
)
kable(coords(
  gr_roc,
  "best",
  best.method = "youden",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "accuracy",
    "tpr",
    "fpr",
    "tnr",
    "fnr"
  )
))
```

>>>>

    "Low",
    "Low",

@@

    "Low",
    "High",

@@

# All genotypes
df$`Detailed Genotype` = paste0(df$Genotypes1, "/", df$Genotypes2)

@@

  levels = c("Cystic Fibrosis", "CFTR-RD or CRMS", "Non-CF")

@@

  levels = c("Not CF", "Low", "High", "Unknown")

@@

# Make detailed genotype table for manuscript
geno_tab = xtabs(
  ~ `Detailed Genotype` + `Genotype Risk` + Diagnosis,
  data = df,
  addNA = T
) |>
  data.frame() |>
  filter(Diagnosis == "Cystic Fibrosis") |>
  select(-Diagnosis) |>
  pivot_wider(names_from = Genotype.Risk, values_from = Freq)
categories = c("Not CF", "Low", "High", "Unknown")
geno_tab$Category = apply(geno_tab[, categories], 1, function(r) {
  w = which(r != 0)
  if (length(w) > 0) {
    return(categories[w])
  } else {
    return(NA)
  }
})
geno_tab$Count = rowSums(geno_tab[, c("Not CF", "Low", "High", "Unknown")])
geno_tab$Percentage = scales::percent(geno_tab$Count / sum(geno_tab$Count))
geno_tab$`Num. CF Participants` = paste0(
  geno_tab$Count,
  " (",
  geno_tab$Percentage,
  ")"
geno_tab = geno_tab |>
  filter(!is.na(Category)) |>
  select(Detailed.Genotype, `Num. CF Participants`, Category) |>
  rename(`Detailed Genotype` = Detailed.Genotype)
  geno_tab,
  file = "./Dissemination/Genotypes.csv",

@@

## Table 2: CF Demographics by Genotype Risk

@@

```{r}
# Fit a multiclass ROC
mc_roc <- multiclass.roc(
  df$Diagnosis,
  df$`Na:Cl`,
  quiet = T,
  levels = c("Non-CF", "CFTR-RD or CRMS", "Cystic Fibrosis")
)
roc_list = mc_roc$rocs
names(roc_list) <- lapply(mc_roc$rocs, function(r) {
  paste(r$levels, collapse = " vs. ")
})
ggroc(roc_list, legacy.axes = T) +
  theme_bw() +
  theme(legend.title = element_blank())
roc_table <- lapply(roc_list, function(r) {
  coords(
    r,
    "best",
    best.method = "youden",
    ret = c(
      "threshold",
      "sensitivity",
      "specificity",
      "accuracy",
      "tpr",
      "fpr",
      "tnr",
      "fnr"
    )
  )
})
roc_table <- do.call(rbind, roc_table)
kable(roc_table, digits = 3)
```

@@

```{r}
plot(
  roc_list[[1]],
  print.auc = T,
  print.thres = T,
  main = names(roc_list)[1]
)
plot(
  roc_list[[2]],
  print.auc = T,
  print.thres = T,
  main = names(roc_list)[2]
)
plot(
  roc_list[[3]],
  print.auc = T,
  print.thres = T,
  main = names(roc_list)[3]
)
```

@@

```{r}
# Fit a multiclass ROC
gr_roc <- roc(
  `Genotype Risk` ~ `Na:Cl`,
  data = df,
  levels = c("Low", "High"),
  quiet = T
)
plot(
  gr_roc,
  print.auc = T,
  print.thres = T,
  main = "Low vs. High Risk Genotype"
)
kable(coords(
  gr_roc,
  "best",
  best.method = "youden",
  ret = c(
    "threshold",
    "sensitivity",
    "specificity",
    "accuracy",
    "tpr",
    "fpr",
    "tnr",
    "fnr"
  )
))
```
